\documentclass[11pt]{article}
\usepackage[a4paper,margin=2.4cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{fancyvrb}
\usepackage[hidelinks]{hyperref}
\setlength{\parskip}{0.5em}
\setlength{\parindent}{0pt}
\newcommand{\OPEN}{\textbf{\textsf{OPEN}}}
\title{\textbf{PDF\_263 --- Yang--Mills Tower Equation Report}\\[0.3em]
\large An Honest, Complete Audit of the YM/OS Witness-Collapse Bricks\\[0.2em]
\normalsize Theorema Aureum 143 (Volume I) --- Morning Star Project}
\author{D.\ Fox \ (ORCID 0009-0008-1290-6105)}
\date{2026-06-03 \quad\textbar\quad Mathlib v4.12.0}
\begin{document}
\maketitle
\thispagestyle{empty}

\begin{center}
\fbox{\parbox{0.92\textwidth}{\small
\textbf{HONESTY NOTICE (read first).}
This report makes \emph{no} claim that the Yang--Mills mass gap is proven,
that $\mu>0$, or that Clay ``Surface~\#1'' is closed. Every one of the 13
modules audited here is currently an \OPEN{} (named, \emph{unproven})
proposition. The axiom footprint is the classical trio
$\{\texttt{propext},\ \texttt{Classical.choice},\ \texttt{Quot.sound}\}$ ---
\emph{not} the empty set. There are no \texttt{sorry}/\texttt{sorryAx}/\texttt{admit}
\emph{proof-terms}. This is logical-hygiene bookkeeping; it proves nothing new.
Sections that earlier drafts requested but for which \emph{no artifact exists on
disk} (an ``LLM error / Z-protocol'' narrative and ``Besel~I'' test logs) are
documented as \textbf{absent} in \S\ref{sec:absent} rather than fabricated.
}}
\end{center}

\tableofcontents
\clearpage
\section{Equation statement --- the Yang--Mills mass-gap surface}
\label{sec:eq}

The Clay ``Yang--Mills existence and mass gap'' problem asks, for a compact
simple gauge group (here $SU(3)$), for a quantum Yang--Mills theory on
$\mathbb{R}^4$ whose Hamiltonian has a strictly positive spectral gap above the
vacuum. The chain of statements the YM/OS modules in this repository attempt to
encode is the following.

\paragraph{(E1) Exponential clustering (two-point decay).}
\[
\bigl|\,\langle W(C_1)\,W(C_2)\rangle - \langle W(C_1)\rangle\,\langle W(C_2)\rangle\,\bigr|
\;\le\; C\,e^{-\Delta\,\mathrm{dist}(C_1,C_2)},
\qquad \Delta>0 .
\]
\begin{itemize}
  \item $W(C)$ --- the Wilson loop observable on a closed contour $C$ (the
        gauge-invariant trace of the parallel transport around $C$).
  \item $\langle\cdot\rangle$ --- the (Euclidean) expectation in the lattice
        Yang--Mills measure.
  \item $\mathrm{dist}(C_1,C_2)$ --- the separation between the two loops.
  \item $\Delta>0$ --- the \emph{mass gap}: the rate of exponential decay of
        connected correlations. Strict positivity of $\Delta$ is the entire
        content of the problem.
  \item $C$ --- a finite positive constant.
\end{itemize}

\paragraph{(E2) Transfer-operator gap.}
Clustering at rate $\Delta$ is equivalent to a spectral gap of the Euclidean
transfer operator $T_{\mathrm{real}}$ acting on the physical Hilbert space:
\[
\operatorname{spec}\!\bigl(T_{\mathrm{real}}\big|_{\mathcal H_0}\bigr)\subseteq[0,\ \lambda_1],
\qquad
\lambda_1 \;=\; \bigl\|\,T_{\mathrm{real}}\big|_{\mathcal H_0}\bigr\| \;<\; 1,
\qquad
\Delta \;=\; -\log\lambda_1 \;>\;0 .
\]
\begin{itemize}
  \item $T_{\mathrm{real}}$ --- the genuine Wilson/heat-kernel transfer operator
        (one time-step Euclidean evolution).
  \item $\mathcal H_0$ --- the orthogonal complement of the vacuum (mean-zero
        sector).
  \item $\lambda_1$ --- the operator norm of $T_{\mathrm{real}}$ restricted to
        $\mathcal H_0$; the second-largest eigenvalue modulus.
  \item $\Delta=-\log\lambda_1$ --- the same mass gap as in (E1).
\end{itemize}

\paragraph{(E3) Mass gap from the gap bound.}
A self-adjoint $T$ on a Hilbert space $H$ has a mass gap $m$ when
\[
\langle x,\,T x\rangle_{\mathrm{re}} \;\ge\; (1-m)\,\|x\|^2
\quad\text{fails strictly on }\mathcal H_0,
\quad\text{equivalently}\quad
\lambda_1 \le e^{-m},\ \ m>0 .
\]
This is the predicate the repository calls \texttt{HasMassGap H T m}.

\paragraph{The honest gap.}
A \emph{non-vacuous} discharge of (E1)--(E3) requires a real $SU(3)$ Wilson
transfer operator with a strictly positive lower bound $T_{\mathrm{real}}>0$.
The ingredients --- $SU(3)$ character theory / a verified heat-kernel transfer
operator --- are \textbf{absent from mathlib v4.12.0}. Consequently
\textbf{no $T_{\mathrm{real}}>0$ is constructible in this repository}, and every
module below was discharged only at a \emph{degenerate witness} (a
\emph{witness collapse}): the correlator taken $\equiv 0$, the operator
$T:=0$ on $H:=\mathbb{C}$, or a reflexive definitional re-wrap. The recorded
$T_{\mathrm{real}}$ lower bound for all 13 modules is therefore \textbf{none}.
\clearpage
\section{Step-by-step audit --- every YM/OS witness-collapse brick}
\label{sec:deriv}

The table below lists all 13 modules audited on the
\textbf{2026-06-03} repair pass. Each was previously registered as a ``brick''
(a landed result in \texttt{scripts/check-towers.sh}); each has now been
converted \emph{in place} from a proved \texttt{theorem}/\texttt{lemma} into a
named open proposition \verb|def <name>_OPEN : Prop := <fully-closed statement>|
and de-registered from the \texttt{BRICKS} array. Status for all: \OPEN{}
(witness-collapse), $T_{\mathrm{real}}$ bound = \textbf{none}.

{\small
\begin{longtable}{@{}r p{3.0cm} p{4.5cm} p{4.6cm}@{}}
\toprule
\# & File & Named open \texttt{Prop} & Witness collapse \\
\midrule
\endhead
1 & \texttt{YM/ClusteringCore.lean} & \texttt{clusters\_zero\_OPEN} & clustering predicate instantiated at constant-zero pair (vacuous) \\
2 & \texttt{YM/MassGapStandin.lean} & \texttt{massGap\_standin\_example\_OPEN} & mass-gap witness is the zero CLM on H := C (vacuous) \\
3 & \texttt{YM/SpectralGapCore.lean} & \texttt{hasMassGap\_zero\_OPEN} & HasMassGap at T := 0 collapses to 0 >= (1-m)*norm\textasciicircum{}2 (vacuous); def HasMassGap preserved \\
4 & \texttt{YM/TransferOperatorBound.lean} & \texttt{transfer\_gap\_zero\_OPEN} & transferGapBound at degenerate operators (vacuous); def transferGapBound preserved \\
5 & \texttt{YM/TwoPointDecay.lean} & \texttt{clustering\_zero\_from\_transfer\_OPEN} & clustering of constant-zero function, hypothesis unused (vacuous); def hasExponentialClustering preserved \\
6 & \texttt{YM/MassGapFromDecay.lean} & \texttt{mass\_gap\_from\_clustering\_zero\_OPEN} & mass gap from constant-zero clustering, zero witness operator (vacuous) \\
7 & \texttt{YM/IntegratedTailReal.lean} & \texttt{integrated\_tail\_le\_exp\_OPEN} & integrated\_tail L m := rexp(-m*L) so bound is reflexive rexp(-m*L) <= rexp(-m*L) (vacuous); def integrated\_tail preserved \\
8 & \texttt{YM/TransferGapReal.lean} & \texttt{transfer\_gap\_real\_OPEN} & real-named transfer gap still discharged at degenerate witness (vacuous) \\
9 & \texttt{YM/MassGapReal.lean} & \texttt{mass\_gap\_from\_transfer\_OPEN} & mass gap from transfer at zero witness on H := C (vacuous) \\
10 & \texttt{YM/ClusteringImpliesGap.lean} & \texttt{clustering\_implies\_gap\_OPEN} & constant-zero antecedent, zero CLM consequent (vacuous) \\
11 & \texttt{YM/TransferImpliesClustering.lean} & \texttt{transfer\_implies\_clustering\_OPEN} & consequent witness is constant-zero function, hypothesis unused (vacuous) \\
12 & \texttt{YM/TailImpliesTransfer.lean} & \texttt{tail\_implies\_transfer\_OPEN} & integrated\_tail and transferGapBound unfold to same inequality; pure definitional re-wrap (vacuous) \\
13 & \texttt{YM/GapToDecay.lean} & \texttt{gap\_to\_decay\_OPEN} & consequent discharged by f t := exp(-m*t), gap hypothesis unused (vacuous) \\
\bottomrule
\end{longtable}}

\paragraph{Reading the columns.}
\textbf{WHAT} --- the file path and the named proposition (namespace
\texttt{TheoremaAureum.Towers.YM.OS}). \textbf{WHY} --- the proposition's role:
each is one link in the (E1)$\to$(E2)$\to$(E3) clustering/transfer/mass-gap
chain of \S\ref{sec:eq}. \textbf{WHERE} --- the $T_{\mathrm{real}}>0$ status:
\textbf{none} for all, because the proof discharges only at a degenerate
witness. \textbf{WHEN} --- the 2026-06-03 repair audit. The full per-file
SHA-256 hashes are in Appendix~\ref{sec:appendix}.
\clearpage
\section{Representative Lean excerpts (verbatim) with English gloss}
\label{sec:excerpts}

These are exact, unedited excerpts of the converted source on disk. They
illustrate the three collapse shapes; the remaining ten modules collapse for
the analogous reasons recorded in \S\ref{sec:deriv}.

\subsection{Mass-gap inhabitedness (\texttt{MassGapStandin.lean})}
\begin{Verbatim}[fontsize=\small,frame=single]
def hasMassGapLowerBound (mu : R) : Prop :=
  exists C : R, 0 < C and 0 < mu

def massGap_standin_example_OPEN : Prop :=
  hasMassGapLowerBound 1
\end{Verbatim}
\textbf{Gloss.} The predicate asserts only ``there exist a positive constant
$C$ and a positive mass $\mu$.'' Witnessing it at $C=\mu=1$ says nothing about
any Yang--Mills correlator. As written the \texttt{\_OPEN} proposition is
trivially satisfiable. (ASCII rendering: \texttt{R}$=\mathbb R$,
\texttt{exists}$=\exists$, \texttt{and}$=\wedge$, \texttt{mu}$=\mu$.)

\subsection{Reflexive tail bound (\texttt{IntegratedTailReal.lean})}
\begin{Verbatim}[fontsize=\small,frame=single]
noncomputable def integrated_tail (L m : R) : R := rexp (-m * L)

def integrated_tail_le_exp_OPEN : Prop :=
  forall (L m : R), 0 <= m -> 0 <= L -> integrated_tail L m <= rexp (-m * L)
\end{Verbatim}
\textbf{Gloss.} Because \texttt{integrated\_tail L m} is \emph{defined} as
$e^{-mL}$, the ``bound'' unfolds to the reflexive $e^{-mL}\le e^{-mL}$ and
closes by \texttt{le\_refl}. The symbol does not refer to any heat-trace
integral; the genuine statement (a real heat-trace tail bounded by an
exponential) is unreachable here.

\subsection{Gap $\Rightarrow$ decay (\texttt{GapToDecay.lean})}
\begin{Verbatim}[fontsize=\small,frame=single]
def gap_to_decay_OPEN.{u} : Prop :=
  forall {H : Type u} [NormedAddCommGroup H] [InnerProductSpace C H] (m : R),
    0 < m -> m < 1 ->
    (exists T : H ->L[C] H, T != 0 and HasMassGap H T m) ->
      hasExponentialClustering (fun t => Real.exp (-m * t)) m
\end{Verbatim}
\textbf{Gloss.} The consequent is discharged by the obvious function
$f(t)=e^{-mt}$ (which trivially satisfies $|f(t)|\le 1\cdot e^{-mt}$) with the
spectral-gap hypothesis \emph{unused}. So the implication holds as written
without using its antecedent --- a witness collapse. It does not show a real
correlator decays from a real spectral gap.
\clearpage
\section{Requested sections with no artifact on disk (documented, not fabricated)}
\label{sec:absent}

Earlier drafts of this report requested an ``LLM Error Information: Z is a
Protocol'' section and a ``Besel~I concretization'' section, each to cite test
runs and a data file. The honesty rule of this project forbids presenting
unrecorded narrative or test results as data. The following were checked on
disk on 2026-06-03 and found \textbf{absent}:

\begin{itemize}
  \item \texttt{symmetry\_error\_rate.csv} --- \textbf{not present} anywhere in
        the workspace.
  \item \texttt{.local/Besel\_I/} (or any \texttt{*esel*} directory) ---
        \textbf{does not exist}.
  \item \texttt{/mnt/data/Report\_263.pdf} / \texttt{/mnt/data/PDF\_263\_*} ---
        \texttt{/mnt/data} \textbf{is not part of this workspace}
        (workspace root is \texttt{/home/runner/workspace}); no prior draft to
        merge exists.
\end{itemize}

There is no recorded ``Z-protocol'' study, ``phase-shift event'', ``Spark Muse''
observation, attributed quotation, or ``Besel~I'' test log in the repository.
Because none of these artifacts exists, these sections are \textbf{omitted}.
Stating their absence here is the honest treatment: the report leaves out no
\emph{true} implication, and fabricates none.
\clearpage
\section{Compliance certificate --- honest}
\label{sec:compliance}

\begin{longtable}{@{}p{6.2cm} p{8.5cm}@{}}
\toprule
Property & Verified value \\
\midrule
Modules audited & 13 (all YM/OS) \\
Non-vacuous $T_{\mathrm{real}}>0$ proofs achieved & \textbf{0} \\
Converted to named open \texttt{Prop} & 13 \\
De-registered from \texttt{BRICKS} & 13 \\
Axiom footprint (each module) & classical trio: \texttt{propext, Classical.choice, Quot.sound} \\
\texttt{sorry} / \texttt{sorryAx} / \texttt{admit} \emph{proof-terms} & 0 / 0 / 0 \\
Compile (direct-lean) & all EXIT 0 \\
Surface \#1 (global YM mass gap) & \OPEN{} \\
\bottomrule
\end{longtable}

\paragraph{Honest caveats on this certificate.}
\begin{enumerate}
  \item \textbf{The axiom footprint is the classical trio, not the empty set.}
        Each \texttt{\_OPEN} proposition references mathlib
        (\texttt{Measure}/\texttt{inner}/\texttt{Real.exp}), which pulls in
        $\{\texttt{propext},\ \texttt{Classical.choice},\ \texttt{Quot.sound}\}$.
        ``No axiom'' would be \emph{false}; ``no \emph{research-grade} axiom
        beyond the trio'' is the true statement.
  \item \textbf{A literal grep is \emph{not} empty.} The strings
        \texttt{sorry}, \texttt{admit}, and \texttt{axiom} occur in the CLAY
        OPEN docstrings of these files (and across the wider tree --- 140 files
        contain at least one of those strings). The honest signal is therefore
        the \emph{proof-term} count (0) plus \texttt{\#print axioms} (trio only),
        \textbf{not} an empty grep.
  \item \textbf{\texttt{lake build} was not run.} The vendored mathlib
        \texttt{v4.12.0} tag is unresolved, so any \texttt{lake}/\texttt{lake env}
        invocation would re-fetch from remote and wipe the oleans. Verification
        used the documented direct-lean bypass (Appendix~\ref{sec:appendix}). No
        ``\texttt{lake build} exits 0'' claim is made.
  \item \textbf{The \texttt{\_OPEN} propositions are trivially satisfiable as
        written.} The degenerate witnesses remain available, so each
        \texttt{\_OPEN} \texttt{Prop} \emph{names} the as-written shape but does
        \textbf{not} assert the genuine YM surface. The conversion removes a
        vacuous landed \emph{theorem}; it manufactures nothing.
\end{enumerate}

\paragraph{Status of the other towers (no per-brick claim made here).}
This report audits the 13 YM/OS modules only. For the record, and per the
project's locked invariants: the YM and Navier--Stokes towers remain
\texttt{Status: Open} at their Clay surfaces (YM Surface~\#1 open; NS Surfaces
\#1/\#2 open, NS frozen); the RH fragment in \texttt{Towers/RH/} is a
\emph{conditional reduction} over two undischarged open hypotheses, not a proof
of the Riemann Hypothesis. No tower in this repository closes a Clay problem.
\clearpage
\section{Appendix --- provenance and verification method}
\label{sec:appendix}

\paragraph{Verification method (verbatim from the build manifest).}
\begin{itemize}
  \item Method: \texttt{direct-lean (LEAN\_PATH over existing oleans; NOT lake)}.
  \item Reason: vendored mathlib v4.12.0 tag unresolved; lake env would re-fetch and wipe oleans.
  \item Axiom check: \#print axioms appended to /tmp copy, compiled with lean <file>.
  \item All EXIT 0: True; all trio-only: True.
\end{itemize}

\paragraph{Per-file SHA-256 (full).}
{\footnotesize
\begin{longtable}{@{}r p{4.2cm} p{9.3cm}@{}}
\toprule
\# & File (under \texttt{Towers/}) & SHA-256 \\
\midrule
\endhead
1 & \texttt{YM/ClusteringCore.lean} & \texttt{f3ceecd3892edd81a760aa8205e947aef57ee273c84ef5be33c3300f8aa9a1fb} \\
2 & \texttt{YM/MassGapStandin.lean} & \texttt{ffa6f5820e6d6fdc6b0af4051582be2508a35e211117d87e24f26eb799e8ee5d} \\
3 & \texttt{YM/SpectralGapCore.lean} & \texttt{fca1de2b085e768a61ef320db8d7d23f546a0f3ddce0b76ccbc3f956eee69e89} \\
4 & \texttt{YM/TransferOperatorBound.lean} & \texttt{ff0bb4887885a10e11ef0e41a46dd801acb0ff5cb58b75d3d613a3d27e10295c} \\
5 & \texttt{YM/TwoPointDecay.lean} & \texttt{516b8fb721a762181a0200f11e8fd01f16ee01c19ae8228fca944ab907234575} \\
6 & \texttt{YM/MassGapFromDecay.lean} & \texttt{b5acbbc0770f6211765989440ec82a88d6d2744ae7a5d45d383eaa1360adaa3b} \\
7 & \texttt{YM/IntegratedTailReal.lean} & \texttt{223a0dacab5f7bc4b871b9a1dbe620d7944af091d7bbd65d6f6f693d68ef8ca2} \\
8 & \texttt{YM/TransferGapReal.lean} & \texttt{bd30cd0f17d3a74ae8870c1fcaf2808a9584d6e77185274760367abda5484ebe} \\
9 & \texttt{YM/MassGapReal.lean} & \texttt{30f0b1b37c510cee3265a1f5e3e2bcccbf04647a500273f28a09902ffcf51fb0} \\
10 & \texttt{YM/ClusteringImpliesGap.lean} & \texttt{acc573093f6dc6b68e7496ebfd99932ba91a63937a5430c5f4e5eadea3ba1626} \\
11 & \texttt{YM/TransferImpliesClustering.lean} & \texttt{3e502bacd4110ed8e52b5ad1841e98c0e45164e974756b013957b092bff7a301} \\
12 & \texttt{YM/TailImpliesTransfer.lean} & \texttt{e0d3ba5d3cbcad9f17cea42a73cc155af00af2dbb91fc0254f70c8016643bd50} \\
13 & \texttt{YM/GapToDecay.lean} & \texttt{ff4b8f5dd357a353982afe08e66afd8036d4eabc526af4d0c8c364828f235dbe} \\
\bottomrule
\end{longtable}}

\paragraph{Source documents.} \texttt{BUILD\_MANIFEST\_v2.7.json},
\texttt{CLAY\_STATUS.md}, \texttt{reports/CLAY\_REPAIR\_2026-06-03.md},
\texttt{provenance/clay\_repair.diff}. This PDF was generated by
\texttt{reports/build\_pdf263.py} directly from those files; every numeric value
above is copied from them or from a command whose result is stated in the body.

\vfill
\begin{center}\small
Generated 2026-06-03 --- honesty-locked.
No mass-gap / $\mu>0$ / Surface-\#1-closed claim is made.
\end{center}
\end{document}
